Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-06-20 main.tex
Add fingerprints

@@

We also ran noisy tournaments in which there is a 5\% chance that an action
is flipped. The best performing strategies in mean payoff are DBS, designed
to correct for noise, followed by two strategies trained
in the presence of noise, Spiteful TFT (TFT but defects indefinitely if the
opponent defects twice consecutively), two strategies trained without noise, then
OmegaTFT (also designed to handle noise).

@@

\begin{table}[!hbtp]
    \centering
        \input{./tex/noisy_scores.tex}
        \caption{Noisy Tournament: Top Ranking Strategies by Median Score in a
        15000 Tournaments with 5\% noise}
        \label{tbl:noisy_score}
\end{table}

@@

>>>>

Using the method of fingerprinting described in \cite{ashlock2008fingerprinting}
\cite{ashlock2009fingerprint}, we can compare
strategies. For the top performing noisy strategies there is a striking similarity
in the fingerprints.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./plots/EvolvedLookerUp2_2_2.png}
        \caption{Fingerprint for EvolvedLookerUp\_2\_2\_2}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./plots/Evolved_HMM_5.png}
        \caption{Fingerprint for Evolved\_HMM\_5}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./plots/Evolved_FSM_16.png}
        \caption{Fingerprint for Evolved\_FSM\_16}
    \end{subfigure}%

    \caption{Comparison of Fingerprints for Noisy Tournament Top 3}
    \label{fig:comparison_fingerprint_noisy}
\end{figure}

@@

We also ran noisy tournaments in which there is a 10\% chance that an action
is flipped. The best performing strategies in mean payoff are DBS, designed
to correct for noise, followed by two strategies trained
in the presence of noise, Spiteful TFT (TFT but defects indefinitely if the
opponent defects twice consecutively), two strategies trained without noise, then
OmegaTFT (also designed to handle noise).

@@

\begin{table}[!hbtp]
    \centering
        \input{./tex/noisy_scores.tex}
        \caption{Noisy Tournament: Top Ranking Strategies by Median Score in a
        15000 Tournaments with 10\% noise}
        \label{tbl:noisy_score}
\end{table}

@@

Using the method of fingerprinting described in \cite{ashlock2008fingerprinting}
\cite{ashlock2009fingerprint}, we can compare
strategies. For the top performing noisy strategies there is a striking similarity
in the fingerprints.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./plots/DBS.png}
        \caption{Fingerprint for DBS}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./plots/Evolved_ANN_5_Noise_05.png}
        \caption{Fingerprint for Evolved\_ANN\_5\_Noise\_05}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{./plots/Evolved_FSM_16_Noise_05.png}
        \caption{Fingerprint for Evolved\_FSM\_16\_Noise\_05}
    \end{subfigure}%

    \caption{Comparison of Fingerprints for Noisy Tournament Top 3}
    \label{fig:comparison_fingerprint_noisy}
\end{figure}
